\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3.2\baselineskip}

### 2017-03-26 paper/ms.tex
addressing some comments from Stello

To demonstrate the applicability of this model, we apply it to infer the
asteroseismic parameters of the giant star KIC~11615890, observed by the
\kepler\ Mission.
The goal of this example is to show that, even for a low signal-to-noise
dataset with a short baseline, it is possible to infer asteroseismic
parameters with formal uncertainties that are consistent with the parameters
inferred with a much larger dataset.
Looking forward to \tess\ \citep{Ricker:2014,Campante:2016}, we measure
$\nu_\mathrm{max}$ and $\Delta\nu$ using only one month of \kepler\ data and
compare our results to the results inferred from the full 4 year baseline of
the \kepler\ mission.
For KIC~11615890, the published asteroseismic parameters measured using several
years of \kepler\ observations are \citep{Pinsonneault:2014}
\begin{eqnarray}
    \nu_\mathrm{max} = 171.94 \pm 3.62 \,\mu\mathrm{Hz} \quad\mathrm{and}\quad
    \Delta\nu = 13.28 \pm 0.29 \,\mu\mathrm{Hz} \quad.
\end{eqnarray}
We randomly select a month-long segment of \kepler\ data, initialize our
\celeriteterm\ model using a grid search in the parameter space, and then use
\emcee\ \citep{Foreman-Mackey:2013} to sample the joint posterior density for
the full set of parameters.
\Figure{astero-corner} shows the marginalized density for $\nu_\mathrm{max}$
and $\Delta\nu$ compared to the results from the literature.

@@

\facility{Kepler}
\software{%
     \project{corner.py} \citep{Foreman-Mackey:2016},
     \project{Eigen} \citep{Guennebaud:2010},
     \project{emcee} \citep{Foreman-Mackey:2013},
     \project{george} \citep{Ambikasaran:2016},
     \project{LAPACK} \citep{Anderson:1999},
     \project{matplotlib} \citep{Hunter:2007},
     \project{numpy} \citep{Van-Der-Walt:2011},
     \project{transit} \citep{Foreman-Mackey:2016a},
     \project{scipy} \citep{Jones:2001}.
}

>>>>

To demonstrate the applicability of this model, we apply it to infer the
asteroseismic parameters of the giant star KIC~11615890, observed by the
\kepler\ Mission.
The goal of this example is to show that, even for a low signal-to-noise
dataset with a short baseline, it is possible to infer asteroseismic
parameters with formal uncertainties that are consistent with the parameters
inferred with a much larger dataset.
Looking forward to \tess\ \citep{Ricker:2014,Campante:2016}, we measure
$\nu_\mathrm{max}$ and $\Delta\nu$ using only one month of \kepler\ data and
compare our results to the results inferred from the full 4 year baseline of
the \kepler\ mission.
Unlike typical giants, KIC~11615890 is a member of a class of stars where the
dipole ($\ell = 1$) oscillation modes are suppressed by strong magnetic fields
in the core \citep{Stello:2016}.
This makes this target simpler for the purposes of this demonstration because
we can neglect the $\ell = 1$ modes and the model proposed above will be an
effective model for the combined signal from the $\ell = 0$ and 2 modes.

For KIC~11615890, the published asteroseismic parameters measured using several
years of \kepler\ observations are \citep{Pinsonneault:2014}
\begin{eqnarray}
    \nu_\mathrm{max} = 171.94 \pm 3.62 \,\mu\mathrm{Hz} \quad\mathrm{and}\quad
    \Delta\nu = 13.28 \pm 0.29 \,\mu\mathrm{Hz} \quad.
\end{eqnarray}
We randomly select a month-long segment of \kepler\ data, initialize our
\celeriteterm\ model using a grid search in the parameter space, and then use
\emcee\ \citep{Foreman-Mackey:2013} to sample the joint posterior density for
the full set of parameters.
\Figure{astero-corner} shows the marginalized density for $\nu_\mathrm{max}$
and $\Delta\nu$ compared to the results from the literature.

@@

This research made use of Astropy, a community-developed core Python package
for Astronomy \citep{Astropy-Collaboration:2013}.

\facility{Kepler}
\software{%
     \project{AtroPy} \citep{Astropy-Collaboration:2013},
     \project{corner.py} \citep{Foreman-Mackey:2016},
     \project{Eigen} \citep{Guennebaud:2010},
     \project{emcee} \citep{Foreman-Mackey:2013},
     \project{george} \citep{Ambikasaran:2016},
     \project{LAPACK} \citep{Anderson:1999},
     \project{matplotlib} \citep{Hunter:2007},
     \project{numpy} \citep{Van-Der-Walt:2011},
     \project{transit} \citep{Foreman-Mackey:2016a},
     \project{scipy} \citep{Jones:2001}.
}
